\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jan M. Kopankiewicz} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+49(0)15120986818  \\ Berlin, Berlin, Germany} 
\address{\href{mailto:jan+cv@kopankiewicz.de}{jan@kopankiewicz.de} \\ \href{https://www.linkedin.com/in/kopankiewicz/}{linkedin.com/in/kopankiewicz} \\ \href{https://jan.kopankiewicz.de}{jan.kopankiewicz.de}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{As a Creative Technologist and Business Developer with over 5 years of experience in IT- and management consulting in Berlin, Frankfurt, and Munich and federally funded academic institutions, Jan specializes in bridging the gap between business needs and technical capabilities. His passion lies in fostering innovation and driving strategic growth through collaborative problem-solving and stakeholder engagement.}


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Senior Associate - Business Developer and Technology Scout} \hfill 2024 - present\\
PricewaterhouseCoopers GmbH WPG - Experience Center \hfill \textit{Frankfurt a.M., Hesse, DE}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Partnership Development with three globally active hyperscaler alliances and national alliances to position the offerings of the consulting services of PwC Germany, the PwC EMEA firms, and the PwC global network.
    \item Guiding and facilitating internal and external planning and development workshops ranging from 6 to 35 participants in Germany, the Netherlands, and Spain.
    \item Research, Development, and Prototyping for emerging technology solutions.
 \end{itemize}

\textbf{Associate - Creative Technologist and Enterprise Architect} \hfill 02/2021 - 2023\\
PricewaterhouseCoopers GmbH WPG - CIO Advisory and Experience Consulting\hfill \textit{Berlin, Berlin, DE}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Upgraded IT-Architecture guiding principles for two federal public service entities and defended and established new rules regarding FOSS solutions, IT accessibility, usability and economical and ecological sustainability.
    \item Development of the firm-internal BXT Enterprise Architecture Framework. 
    \item Preparation for Business Continuity Management (BSI 200-4) for multiple clients.
     \item Leading an internal developer community for immersive technology and partnership development.
     \item Organization and facilitation of multiple (virtual) international community events for topics on emerging technologies.
    \item Prototype development for the pharmaceutical and automotive industry.
    \item Guiding and facilitating internal and client-facing workshops and learning and development projects.
 \end{itemize}

 \textbf{Research Assistant} \hfill 10/2018 - 01/2021\\
Fraunhofer Institute for Open Communication Systems - ESPRI \hfill \textit{Berlin, Berlin, DE}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Academic research: Developed and implemented research prototypes in human-machine interaction. and contributed to scientific publications and participant studies.
    \item Fraunhofer Academy: Advanced the "Cybersecurity Learning Lab" for IT professionals, and created training content on data protection, privacy, online surveillance, and cybersecurity.
    \item Researched technical feasibility for project and funding applications.
    \item   Scientific Council, Weizenbaum Institute: Advised the Directorate on strategic and scientific priorities, research formats, and knowledge transfer initiatives.
  - Collaborated with Principal Investigators, research group leaders, scientific staff, student assistants, and administrative personnel.

 \end{itemize}

 \textbf{Student Assistant} \hfill 09/2017 - 09/2018\\
University of Potsdam - Chair for Social Media and Data Science \hfill \textit{Potsdam, Brandenburg, DE}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Administrative and marketing tasks during the establishment of the Weizenbaum Institute in Berlin on behalf of the University of Potsdam.
     \item Assisted the research groups "Digital Technologies and Well-being" and "Digital Integration" with research and information gathering activities and testing and development of an Industry 4.0 automated product.
 \end{itemize}
\end{rSection} 


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{@{}>{\bfseries}  l  @{\hspace{5ex}}>{\raggedright\arraybackslash}p{0.7\linewidth}} 
Technical Skills & Python, Hyperscaler Cloud Infrastructure Management, Data Science, Go-to-Market (GTM) Strategy, Market and User Research, Project Management\\ 
Soft Skills & Negotiation Management, Conflict resolution and Mediation, Agile Team Leadership, Community Leading, Partnership Management.\\ 
 Corporate Creative Skills&Workshop Facilitation, Prototyping and Rapid Prototyping, User Testing, Emerging Technology Discovery Workshop, Sustainable Innovation, Creative Problem Solving\\

\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Science - Information Systems}, University of Potsdam, DE\hfill {2016 - 2020}\\
First place in an international negotiation battle. Conducted technology management and foresight analysis for Rohrbeck Heger GmbH. Developed an online marketing strategy for a Berlin-based B2B startup. Conceptualized and developed logistics prototypes, showcasing expertise in process optimization and innovation. Facilitated a strategic foresight methods workshop for a Leibniz Institute, enabling them to identify emerging trends and opportunities. Completed an IT consulting project, "Performance Appraisal Evaluation of Consulting Firms," providing data-driven recommendations for process improvement.
 \begin{itemize}
    \itemsep -2pt {} 
     \item Core Coursework: Data Science, Business Development, Innovation Management.
     \item Master's Thesis: \textit{Modeling of Workflow Processes Aided by Computer Vision}
 \end{itemize}

{\bf Bachelor of Science - Business Administration}, University of Potsdam, DE \hfill {2012 - 2016}\\
Developed an audience-response tool at the Free University Berlin, streamlining real-time feedback collection and analysis.
Contributed to the marketing strategy and event management for a sustainable e-commerce startup, supporting their growth and brand awareness. Demonstrated leadership skills by leading teams of up to 9 students in hands-on marketing projects, fostering collaboration and driving results.
 \begin{itemize}
    \itemsep -2pt {} 
     \item Core Coursework: Sustainable Marketing Management, Innovation and Technology Management, B2B Marketing Management, Business Process Management
     \item Bachelor's Thesis: \textit{Risk Calculation for Enterprise Cyber Security Incidents}
 \end{itemize}


\end{rSection}


%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf {Research Papers on Privacy, Security, and Sonification.} {Aided federally funded research and developed technical software and hardware demonstrators for interactive password strength sonification, online privacy and tracking, and cyber security trainings. (Open accessible paper at \href{https://publica.fraunhofer.de/entities/publication/dc1169a4-f113-49da-9ba5-2c5249e698db/details}{Fraunhofer Publication})
\item  \textbf{GenAI Telephone - Retrofitting a rotary dial Telephone.} {Conceived and build a hardware demonstrator showcasing responsible AI usage, AI Ethics, Anthropomorphism of Generative AI, and data and information validity as a conversation started.  (Link to the \href{https://github.com/030jmk/genAI-telephone}{GitHub Repository})}
\item \textbf{Presifeed - Audience Response System.} {Bootstrapped and developed an audience response tool for universities and events capable of handling hundreds of anonymous users on affordable hardware and cloud infrastructure. (Read an interview about the project in German \href{https://www.tagesspiegel.de/berlin/bezirke/wer-nicht-fragt-bleibt-dumm-4419793.html}{here})}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXTRA CURRICULAR ACTIVITIES
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item Teamer at Lebenshilfe Berlin e.V. a service for indivuals with disabilities
    \item (Beach-)volleyball, swimming, bouldering, running
    \item Former football referee for the Berliner Fußball-Verband e.V via FC Viktoria 1889 Berlin
    \item Former subject matter expert for public safety and (cyber-) security for the grassroots think tank Polis180 e.V.
    
\end{itemize}
\end{rSection}




\end{document}
